Paper NA

### 2017-03-01 Paper_NA_br.tex
Update 01.03.17

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage[english]{babel} 
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{natbib} % Powerful citation management
\bibpunct[; ]{(}{)}{,}{a}{}{;} % Custom minimal bibliography styling
\renewcommand{\baselinestretch}{2}\normalsize
\author{Pierre}
\title{Paper NA}
\date{\today}

@@

\begin{figure}[p]
	\centering
	\centerline{\includegraphics[viewport=180 340 480 570,clip=true,width=\linewidth]{figures/Geologicalmap_Clouzet.pdf}}

	% bb=llx lly urx ury :

	\caption{\baselineskip 18pt
	Large scale Precambrian architecture of North America (modified from \cite{whitmeyer2007tectonic}. Colours indicate ages of different regions, as shown in the legend. The stable cratonic core is defined by the Rocky Mountain Front to the west (dashed dark grey line), defined by the surface trace of deformation), and the appalachian fron to the east (solid light red line). The solid blue line demarcates the westward extent of the Grenville/Llano Front. The solid red line along the Cordillera province demarcates the breakup of Rodinia. Solid green lines indicate tectonic plate boundaries. Abreviations are as follows: RW, re-worked; GBA, Great Bear Arc; BHT, Buffalo Head Terrane; Taltson, Talston Arc; Rimbey, Rimbey Arc; Tornagat, Torngat Arc; L.B.A, Little Belt Arc; LRA; THO, Trans-Hudson Orogen; RGR, Rio Grande Rift; Reelfoot, Reelfoor Rift; Kwn.R, Kewanowan Rift; Sask, Sask Craton; WY, Wyoming Province; Med. Hat., Medicine Hat Block; Grt. Rhy, Granite–Rhyolite Province; Grenville, Grenville Province.
	}

@@

\begin{figure}[p]
	\centering
	\begin{tabular}{ccc}
		\includegraphics[width=1\textwidth]{figures/map_events_stn_global.png}
	\end{tabular}

@@

\begin{figure}[p]
	% bb=llx lly urx ury :
	\begin{minipage}{0.47\linewidth}
		\centerline{\includegraphics[viewport=120 10 470 420,clip=,width=\linewidth]{figures/Coverage_L_iter3.png}}
	\end{minipage}
	\hfill
	\begin{minipage}{0.47\linewidth}
		\centerline{\includegraphics[viewport=120 10 470 420,clip=,width=\linewidth]{figures/Coverage_T_iter3.png}}
	\end{minipage}

@@

\begin{figure}[p]
% \centering
	\begin{tabular}{ccc}
		(a)&&(b)\\
		\includegraphics[width=.4\textwidth]{figures/snap_glob.pdf} && \includegraphics[width=.4\textwidth]{figures/snap_reg.pdf} \\ 
		\includegraphics[width=.4\textwidth]{figures/seismo.pdf}    && \includegraphics[width=.4\textwidth]{figures/seismo.pdf}
	\end{tabular}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\textwidth]{figures/Vs-60-300-for-paper.png}

	\caption{\baselineskip 18pt
	3D isotropic shear wave velocity structure of the continent. Map views are shown from 60 km down to 300 km, shown as variations with respect to the regional mean (thick red line in Figure ~\ref{1daverage}). 
	% Labels are: BP, Blake Plateau; NQ, New Quebec Orogen; THO, Trans-Hudson Orogen. State abbreviations are: CO, Colorado; MT, Montana; ND, North Dakota; SD, South Dakota; and WY, Wyoming. 
	% The geological limits of the cratonic crust are indicated as follows: (to be defined when using final figures... 
	}

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\textwidth]{figures/Xi-60-300-for-paper.png}

	\caption{\baselineskip 18pt
	3D isotropic radial anisotropy structure of the continent. Map views are shown from 60 km down to 300 km, shown as variations with respect to the regional mean (thick red line in Figure ~\ref{1daverage}). 
	% Labels are: BP, Blake Plateau; NQ, New Quebec Orogen; THO, Trans-Hudson Orogen. State abbreviations are: CO, Colorado; MT, Montana; ND, North Dakota; SD, South Dakota; and WY, Wyoming. 
	% The geological limits of the cratonic crust are indicated as follows: (to be defined when using final figures... 
	}

@@

\subsection{Continental model}
\begin{figure}[ht]
	\centering
	\includegraphics[width=1\textwidth]{figures/1D_profile_with_regions.png}

@@

I am on this part..

@@

\begin{figure}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_A.pdf}}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_B.pdf}}
	\end{minipage}

@@

Our study confirms the presence of a thick lithospheric root in the craton with faster than average $V_S$ down to $250km$ depth, with highest velocities, ca. $4.8km.s^{-1}$, located at depths shallower than  $150km$ (e.g. Figure~\ref{cratoncross}). 
Laterally, the cratonic root in $V_S$ coincides roughly with precambrian aged crust (see Figure~\ref{3d-VS} from 60 to 150km deep)
The western edge of the craton follows the RMF (black thick dashed line in Figure \ref{mapgeol}), instead of the western breakup line (See the red thin line in Figure~\ref{mapgeol} which coincides with RMF in Canada, but is diverging westward in the U.S.). While the eastern/south-esatern coincides with the Llano-Grenville Front (See the blue thin line in Figure~\ref{mapgeol}). 
The northern part ends at the coastline of the Arctic ocean including the arctic archipelago and Greenland.

@@

As observed in \cite{babuvska1998age,gung2003global,yuan2014lithospheric}, there are large lateral variations  $\xi$ down to $\sim 200km$ depth, with regions of reduced radial anisotropy, in contrast to the more uniform, positive $dln(\xi)$ structure in this depth range in the oceans (See figure \ref{3d-Xi}. 
Below 250km, it is interesting to note that there is a large band of positive anomaly crossing the whole continent (across the US), making the connection between the Pacific and Atlantic mantles.

Generally, $\xi$ always appear higher than 1. 
Except around 100 km, negative absolute values of $\xi$ (lower than -$1\%$) are observed in Mexico, at the southern part of Florida, the southern part of the Superior craton comprising the Mid Continental rifting, the southern part of the Granit Rhyiolite Province comprising the Failed Rifting area and finally beneath Baffin Island.

\subsubsection{Wyoming}{h}
% \begin{figure}
% 	\begin{minipage}{0.5\linewidth}
% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_wyoming_A.pdf}}
% 	\end{minipage}
% 	\hfill
% 	\begin{minipage}{0.5\linewidth}
% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_wyoming_B.pdf}}
% 	\end{minipage}

% 	\caption{Cross Section of the Wyoming lithosphere}
% 	\label{wyomingcross}

% \end{figure}

The Archaean aged Wyoming craton does not show as high anomalies as within the craton nucleus as shown in figure ~\ref{3d-VS}. 
It is split into 2 distinctive part. A western part showing low velocities influenced by the active tectonic with a radially positive gradient. 
In contrast with the eastern part showing higher velocities with a radially negative then positive gradient. 
The depth of negative gradient's minima is variable, from 70 (western part) to 250km (eastern part) deep. 
The separation between the two areas coincides with the RMF.

\subsubsection{Slave}

	% \begin{figure}
	% 	\begin{minipage}{0.5\linewidth}
	% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_slave_A.pdf}}
	% 	\end{minipage}
	% 	\hfill
	% 	\begin{minipage}{0.5\linewidth}
	% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_slave_B.pdf}}
	% 	\end{minipage}

	% 	\caption{Cross Section of the Slave lithosphere}
	% 	\label{slavecross}

	% \end{figure}

	The Archaean aged Slave craton shows typical lithospheric craton signatures with higher than average velocities as shown in figure ~\ref{3d-VS} and in figure~\ref{cratoncross}. 
	It shows in the entire region a positive velocity gradient with a maximum of ca. $4.8km.s^{-1}$ associated with a maximum of $\xi$ at ca. $150km$ deep.
	Deeper, a negative gradient is observed with a minimum of ca. $4.6km.s^{-1}$ at ca. $250km$ deep. 
	The topography of the extrema appears flat. (Est ce que c'est une characteristique d'un craton stable non deforme?)
	Although the Slave lithosphere shows highest velocities at $150km$, above $100km$ velocities are slightly higher than the continental average ($dln(V_S)< 4\%$).

\subsubsection{Superior Craton}
	In our model, the Superior craton can be split in two parts: The western part showing typical cratonic structures while the eastern part shows slower velocities at all depths. Below $150km$, velocity anomalies are below $2\%$ (almost $0\%$).

	\paragraph{Western part}
		% \begin{figure}
		% 	\begin{minipage}{0.5\linewidth}
		% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_west_superior_A.pdf}}
		% 	\end{minipage}
		% 	\hfill
		% 	\begin{minipage}{0.5\linewidth}
		% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_west_superior_B.pdf}}
		% 	\end{minipage}

		% 	\caption{Cross Section of the western Superior lithosphere}
		% 	\label{westsupcross}

		% \end{figure}

		The Archaean aged Superior craton shows typical lithospheric craton signatures with higher than average velocities as shown in figure ~\ref{3d-VS} and in figure~\ref{cratoncross}. 
		It shows in the entire region a positive velocity gradient with a maximum of ca. $4.8km.s^{-1}$  associated with a maximum of $\xi$ at ca. $150km$ deep.

		Deeper a negative gradient is observed with a minimum of ca. $4.6km.s^{-1}$ at ca. $250km$ deep. 
		Opposed to the Slave craton, the topography of the extrema is variable. 
		From SW to NE, the core of maximum velocity can reach beween 70 and 150km of thickness. 
		Beneath the maximum velocity region of ca. $150km$ the negative gradient appears stipper than beneath the $70km$ one, while the topography of the deeper positive gradient appears flat. 
		At the south-eastern part of the western Superior, close the Mid-Lithospheric rift, we can observe the thinning of the cratonic lithosphere when crossing the Grenville front. 
		The band of minimum velocity within the cratonic root has similar amplitudes, in terms of velocity, than beneath the younger lithosphere but at shalower depths between $100$ and $150km$. 
		Following the Great Meteor track built by \cite{heaman2000timing}, which crosses the Superior craton, it is interseting to note that the low velocity channel beneath the base of the lithosphere shows lower velocties than usualy observed beneath the other Archaean cratons. 
		This slow anomaly corresponds to the V-shape dent, or divot, observed by \cite{lee1997upper} who explained the feature by the presence of water in the mantle. 
		We observe at $250km$ that the slow anomaly go further inland and crosses the Superior Craton northward until the Hudson bay following the GMT.

		\paragraph{Eastern part}
		% \begin{figure}
		% 	\begin{minipage}{0.5\linewidth}
		% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_east_superior_A.pdf}}
		% 	\end{minipage}
		% 	\hfill
		% 	\begin{minipage}{0.5\linewidth}
		% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_east_superior_B.pdf}}
		% 	\end{minipage}

		% 	\caption{Cross Section of the western Superior lithosphere}
		% 	\label{eastsupcross}

		% \end{figure}

		Compared to its western part, the structure here shows differences as shown in figure ~\ref{cratoncrossedge} 
		Fast velocities are present down to $150km$deep but are slower. 
		The negative gradient is steeper and the minimum is radially thicker. 
		However at the center, the minimum channel is not continuous and shows higher (still slower than the center of the western Superior) velocities.
		% the gradual trend in velocity is replaced by an almost constant slow anomaly from $150$ to $300km$ deep.

\subsubsection{Trans Hudson Orogen}
	The Trans Hudson Orogen (THO) is a belt of Paleo-Proterozoic aged region. It refers to a major tectonic event (between $2.0$ to $1.8Ga$) that welded Archaean blocks to form the Laurentia Craton.
	% At shallow depths ($ < 60km$) shows lower velocities than archaean surroundings. 
	It is interesting to notice that at shallower depths than $100km$, the proterozoic THO (including the Sask craton) which welded the Superior and Rae/Hearne cratons, shows lighter (i.e, $+4\%$ compared to $+8\%$) positive anomalies than its archaean surrounding. While most of the proterozoic root start to thin out at $150km$, the THO at the vicinity of the hudson bay shows as high anomalies as Rae/Hearne and Superior areas. 
	Je suis en train de construire des profils le long de THO pour voir!

\subsubsection{Yavapai/Mazatzal/Granit-Rhyolite region}
	% \begin{figure}
	% 	\begin{minipage}{0.5\linewidth}
	% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_yava-maza_A.pdf}}
	% 	\end{minipage}
	% 	\hfill
	% 	\begin{minipage}{0.5\linewidth}
	% 		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_yava-maza_B.pdf}}
	% 	\end{minipage}

	% 	\caption{Cross Section of the Yavapai and Mazatzal lithosphere}
	% 	\label{yavacross}

	% \end{figure}

\subsection{Surrounding oceanic} This section needs to be redone...

	Our inversion is focusing on the continental part, as shown in our spatial parameterization (i.e. see figure~\ref{density_coverage}) where the region is sampled by data.
	Ecxept the oceanic borders of NA, further away, the structure has not been updated from SEMucb\_wm1 \citep{french2014whole}.

	\subsubsection{Eastern Passive margin}
		As in \cite{schaeffer2014imaging,yuan2014lithospheric,james2014rayleigh,silveira2002anisotropic,mocquet1990three}, we observe along the negative anomaly structure following the Appalachian continental shelf, a stretched positive anomaly structure from the Suwanne terrane in Florida to the Avalonian terranes of New-Scotland. 
		At $60km$ it is made of several blocks of at most $+3\%$ anomalies emdedded in a $+2\%$ structure. At $150km$, the structure is split into 2 blocks by a slow anomaly comprising both the Great Meteor (GMT) and Bermuda tracks, and further southeast, the Low Velocities Fingers (LVF) observed in \cite{french2013waveform}.

		Such structure would correspond to late proterozoic gondwanian continental terranes that formed during the Pan African orogenesis \citep{kennedy1964structural} and remained attached to the North American margin during the opening of the Atlantic ocean. \citep[e.g.][]{thomas2006tectonic}
		On the continental shelf, authors \citep[e.g.][]{o1983avalon,nance2002cordilleran} identified the west Avalonian terranes of pan-african affinity as in Florida \citep[see][]{smith1982review} that might have been underlayed by a thin (ca. $100km$) lithosphere before the Pangaea assembling. \citep{mckenzie2015lithospheric}

		Fast anomalies are observed beneath the whole gulf of Mexico down to $150km$ deep. Despite the proximity with pan-african lithosphere, such high velocity anomalies represent older than $ca. 150Ma$ oceanic lithosphere. \citep{muller2008age,pindell2009tectonic}
		-- No Magnetic anomalies recorded as in Pan African, Oceanic seafloor according to Pindel --

\subsubsection{The Great Meteor track}
	\begin{figure}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_GMTrack.pdf}}

@@

	\cite{davies1994thermomechanical} described a process of thermo-mechanical erosion which involves heating-softening of the lithospheric base by a plume tail, followed by mechanical removal of the material due to convective transfer. \citep{rondenay2000lithospheric}
% This hypothesis is based on different points:
% \begin{itemize}
% \item The lithosphere is moving above a fixed mantle where plume originate \citep[e.g.][]{morgan1972deep}
% \item Age progression along seamounts \citep[see for example][]{crough1980kimberlites,morgan1983hotspot,duncan1984age,sleep1990monteregian}
% \item Concordance between kimberlite ages and the continental drifting rate of North America. \citep{crough1980kimberlites,duncan1984age}
% \item Evidence of hotspot related uplift along both continental and oceanic structures. \citep{crough1981mesozoic,sleep1990monteregian}
% \item Similarities in initial Sr and Nd isotopic ratios between land and sea portions. (Foland et al., 1988)
% \end{itemize}

% Continuity: 
% Chercher anomalie de flux thermique (Jaupart 2000 2002 2014) ne montrent rien
% Parler de l'hypothese rifting of the continental plate qui est en opposition avec Mantle plume.
% -- Lien avec Vs (effet thermique/chimique/fabrics) ou il faudrait prendre en compte les effets anharmonicity/anelasticity. Voir Ebinger et Sleep 1998
% -- Haydar voit une anomalie negative de Q dans la region Great Meteor + Finger!! 
% -- Trouver model de conductivite, anomalie de Gravi? Pour appuyer 
% -- Faire le lien avec Kaban 2015 Byriol 2016 Poritt 2014
% -- Fingers From SEMum2 se dirigent plus vers le Bermuda hotspot que GMT, Meme si il y a un lien entre les 2 a 150km.
% -- Aucune update du Model de GMT depuis Haeman 2000...
% This feature, parrallel the Absolute Plate Motion (APM) corresponds to the Low Velocity Fingers (LVF) introduced by \cite{french2013waveform} and it shows highest negative anomalies between $100km$ and $200km$ and seems to vanish below $250km$. While in \cite{french2013waveform}, the North Atlantic LVF was stopped at the shelf of the US, our model shows that the slow velocity anomaly goes further through the continental lithosphere with a contrast of $-2\%$ to $-3\%$ compared to the surrounding cratonic root. This slow anomaly corresponds to the V-shape dent, or divot, observed by \cite{lee1997upper}.

% Some authors [Sykes,1978; Croughet al., 1980] have suggested a genetic relation between
% kimberlites and hotspot tracks, here defined as lin-
% ear, anorogenicvolcanic chains mapped over oceanic
% and young continental lithospheres. The termination
% of these features over thickening continental roots has been cited as evidence supporting the origin of hotspot tracks in the interaction of fixed mantle plumes with an overriding plate [Morgan,1972;Burke and Wilson,
% 1976; Crough et al., 1980; Sleep, 1990a; Duncan and
% Richards, 1991], although compelling arguments may also be made for association of hotspot tracks with an-
% cient rifts and subvertical lithospheric discontinuities [Curtie,1976;Sykes,1978;Anderson1,998

% Hotspot tracks preserve records of past plate motion and provide markers with which the relative motion between a plate’s surface and underlying mantle regions may be examined

% Quand tu vas parler de l'implication thermale et chimqieu il faut citer le boulot de Haydar avec son anomalue negative de Q.

% At least two Mesozoic hotspot tracks have been postulated for eastern North America; the Juras- sic Verde and Cretaceous Great Meteor tracks [38^40,42,43]. According to Morgan [39], these two parallel and closely spaced hotspot tracks passed through Ontario and the New England region at slightly di¡erent times (c. 40 Myr apart). The location of the continental portion of these tracks is based on several lines of evidence includ- ing: (1) the current position of Atlantic Ocean hotspots; (2) the record of ocean £oor magnetic anomalies; (3) the assumption that the position of hotspots remains relatively ¢xed on Earth with time; and (4) the relative motions of North Amer- ica, South America, and Africa during the various stages recorded in opening of the Atlantic Ocean since about 200 Myr [50]. In the case of these Atlantic hotspots, the initial portion of the track typically begins on the continent and eventually moves toward the current oceanic position of the corresponding mantle plume.

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage[english]{babel} 
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{natbib} % Powerful citation management
% \usepackage{float}
% \floatplacement{figure}{p}
\bibpunct[; ]{(}{)}{,}{a}{}{;} % Custom minimal bibliography styling
\renewcommand{\baselinestretch}{2}\normalsize
\author{Pierre}
\title{Paper NA}
\date{\today}

@@

@@

@@

@@

@@

@@

	\subsection{Continental model}

@@

@@

		Our study confirms the presence of a thick lithospheric root in the craton with faster than average $V_S$ down to $250km$ depth, with highest velocities, ca. $4.8km.s^{-1}$, located at depths shallower than  $150km$ (e.g. Figure~\ref{cratoncross}). 
		Laterally, the cratonic root in $V_S$ coincides roughly with precambrian aged crust (see Figure~\ref{3d-VS} from 60 to 150km deep)
		The western edge of the craton follows the RMF (black thick dashed line in Figure \ref{mapgeol}), instead of the western breakup line (See the red thin line in Figure~\ref{mapgeol} which coincides with RMF in Canada, but is diverging westward in the U.S.). While the eastern/south-eastern coincides with the Llano-Grenville Front (See the blue thin line in Figure~\ref{mapgeol}). 
		The northern part ends at the coastline of the Arctic ocean including the arctic archipelago and Greenland.

		As observed in \cite{babuvska1998age,gung2003global,yuan2014lithospheric}, there are large lateral negative variations $\xi$ down to $\sim 200km$ depth, with regions of reduced radial anisotropy, in contrast to the more uniform, positive $dln(\xi)$ structure in this depth range in the oceans (See figure \ref{3d-Xi}. 
		Below 250km, it is interesting to note that there is a large band of positive anomaly crossing the whole continent (across the US), making the connection between the Pacific and Atlantic mantles. 
		This feature is not present in most of Canada, where negative $dln(\xi)$ structure persist down to 300km.
		Generally, $\xi$ always appear higher than 1. 
		Except between 60 and 100 km, lower than 1 of $\xi$ ($V_{SV} > V_{SH}$) are observed in Mexico, at the southern part of Florida, the southern part of the Superior craton comprising the Mid Continental rifting, the southern part of the Granit Rhyiolite Province comprising the Failed Rifting area, a large area comprising southern Hearne, Medicine hat, northern Wyoming, B.H.T, Cordillera; and finally beneath Baffin Island. This feature can be better observed in Figure \ref{3d-xi-iso-100km} where perturbations are shown according the Isotropic case ($\xi = 1$)

	\subsubsection{Archaean provinces}

		\paragraph{Wyoming and Medecine Hat}
			The highly reworked Wyoming craton does not show as high anomalies as within the craton nucleus (+2\% intstead of +4-8\%) as shown in figure ~\ref{3d-VS}. 
			It is split into 2 distinctive part. A western part showing low velocities influenced by the active tectonic with a radially positive gradient. 
			In contrast with the eastern part showing higher velocities with a radially negative then positive gradient which marks the western border of the craton nucleus. 
			The depth of negative gradient's minima is variable, from 70 (western part) to 250km (eastern part) deep. 
			The separation between the two areas coincides with the RMF.
			In terms of $\xi$, it is characterized by negative anomalies down to 250km deep. 
			The northern part shows highest anomalies and $V_{SV}$ appears higher than $V_{SH}$ of about 2\% between 60 and 100km. This feature is common with the Medicine Hat province (See Figure \ref{3d-xi-iso-100km}).

		\paragraph{Slave}
			The Slave craton shows typical lithospheric craton signatures with higher than average velocities (See figures \ref{3d-VS} and \ref{cratoncross}), and negative perturbations of $\xi$ (See Figure \ref{3d-VS}. 
			We can note that the average of $\xi$ is the only one higher than the continental mean, compared to the other Archaean provinces (See Figure \ref{1daverage}.
			It shows in the entire region a positive velocity gradient with a maximum of ca. $4.8km.s^{-1}$ associated with a maximum of $\xi$ at ca. $150km$ deep. 
			Deeper, a negative gradient is observed with a minimum of ca. $4.6km.s^{-1}$ at ca. $250km$ deep. 
			The topography of the extrema appears flat.
			Although the Slave lithosphere shows highest velocities at $150km$, above $100km$ velocities are slightly higher than the continental average ($dln(V_S)< 4\%$).

		\paragraph{Superior Craton}
			In our model, the Superior craton can be split in two parts: The western part showing typical cratonic structures while the eastern part shows slower velocities at all depths. Below $150km$, velocity anomalies are below $2\%$ (almost $0\%$).

		\paragraph{Western part}
			The western Superior craton shows typical lithospheric craton signatures with highest velocities as shown in figure ~\ref{3d-VS} and in figure~\ref{cratoncross}. In terms of $\xi$, slight negative to zero perturbations are observed at the very western part, while close to the Mid continental rifting, highest negative perturbations indicate that $V_{SV}$ is higher than $V_{SH}$. This last feature is associated the thinning of the cratonic lithosphere when crossing the Grenville front.
			In the entire region there is a positive velocity gradient with a maximum of ca. $4.8km.s^{-1}$  associated with a maximum of $\xi$ at ca. $150km$ deep.

			Deeper a negative gradient is observed with a minimum of ca. $4.6km.s^{-1}$ at ca. $250km$ deep. 
			Opposed to the Slave craton, the topography of the extrema is variable. 
			From SW to NE, the core of maximum velocity can reach beween 70 and 150km of thickness. 
			Beneath the maximum velocity region of ca. $150km$ the negative gradient appears stipper than beneath the $70km$ one, while the topography of the deeper positive gradient appears flat.

			The band of minimum velocity within the cratonic root has similar amplitudes, in terms of velocity, than beneath the younger lithosphere but at shalower depths between $100$ and $150 \: km$. 
			Following the Great Meteor track built by \cite{heaman2000timing}, which crosses the Superior craton, it is interseting to note that the low velocity channel beneath the base of the lithosphere shows lower velocties than usualy observed beneath the other Archaean cratons. 
			This slow anomaly could correspond to an extension the V-shape dent, or divot, observed by \cite{lee1997upper} who explained the feature by the presence of water in the mantle. 
			We observe at $250km$ that the slow anomaly go further inland and crosses the Superior Craton northward until the Hudson bay following the GMT.

		\paragraph{Eastern part}
			Compared to its western part, the structure here shows differences as shown in figure ~\ref{cratoncrossedge} 
			Fast velocities are present down to $150 \: km$ deep but are slower and no perturbations are observed below $200 \: km$. 
			The negative gradient is steeper and the minimum is radially thicker (more than $100 \: km$ thick compare to $\sim 50 \: km$ beneath the craton nucleus). 
			% However at the center, the minimum channel is not continuous and shows higher (still slower than the center of the western Superior) velocities.
			% the gradual trend in velocity is replaced by an almost constant slow anomaly from $150$ to $300km$ deep.

		\paragraph{Trans Hudson Orogen}
			The Trans Hudson Orogen (THO) is a belt of reworked archaean aged region. It refers to a major Paleo Proterozoic tectonic event (between $2.0$ to $1.8Ga$) that welded the Hearne, Wyoming, and Superior archaean blocks to form core of Laurentia \citep{hoffman1988united,whitmeyer2007tectonic}.
			% At shallow depths ($ < 60km$) shows lower velocities than archaean surroundings. 
			It shows typical lithospheric craton signatures with higher than average velocities (See figures \ref{3d-VS} and \ref{cratoncross} associated with negative $\xi$ perturbations. 
			It is interesting to notice that at shallower depths than $100km$, the THO (including the Sask craton) which welded the Superior and Rae/Hearne cratons, shows lighter (i.e, $+4\%$ compared to $+8\%$) positive anomalies than its archaean surrounding. This feature is associated with negative anomalies of $\xi$. While most of the proterozoic root start to thin out at $150km$, the THO at the vicinity of the hudson bay shows as high anomalies as Rae/Hearne and Superior areas associated with zero to positive anomalies in term of $\xi$.

	\subsubsection{Yavapai/Mazatzal/Granit-Rhyolite region}

\subsubsection{Surrounding oceanic} This section needs to be redone...

	Our inversion is focusing on the continental part, as shown in our spatial parameterization (i.e. see figure~\ref{density_coverage}) where the region is sampled by data.
	Except the oceanic borders of NA, further away, the structure has not been updated from SEMucb\_wm1 \citep{french2014whole}.

	\subsubsection{Eastern Passive margin}
		As in \cite{schaeffer2014imaging,yuan2014lithospheric,james2014rayleigh,silveira2002anisotropic,mocquet1990three}, we observe along the negative anomaly structure following the Appalachian continental shelf, a stretched positive anomaly structure from the Suwanne terrane in Florida to the Avalonian terranes of New-Scotland. 
		At $60km$ it is made of several blocks of at most $+3\%$ anomalies emdedded in a $+2\%$ structure, associated with zero to positive $\xi$ anomalies. At $150km$, the structure is split into 2 blocks by a slow anomaly comprising both the Great Meteor (GMT) and Bermuda tracks, and further southeast, the Low Velocities Fingers (LVF) observed in \cite{french2013waveform}.

		Such structure would correspond to late proterozoic gondwanian continental terranes that formed during the Pan African orogenesis \citep{kennedy1964structural} and remained attached to the North American margin during the opening of the Atlantic ocean. \citep[e.g.][]{thomas2006tectonic}
		On the continental shelf, authors \citep[e.g.][]{o1983avalon,nance2002cordilleran} identified the west Avalonian terranes of pan-african affinity as in Florida \citep[see][]{smith1982review} that might have been underlayed by a thin (ca. $100 \: km$) lithosphere before the Pangaea assembling. \citep{mckenzie2015lithospheric}

		Fast veolicity associated with typical oceanic radial anisotropic structures are observed beneath the whole gulf of Mexico down to $150 \: km$ deep. Despite the proximity with pan-african lithosphere, such high velocity anomalies represent older than $\sim 150 \: Ma$ oceanic lithosphere. \citep{muller2008age,pindell2009tectonic}
		-- No Magnetic anomalies recorded as in Pan African, Oceanic seafloor according to Pindel --

\subsubsection{The Great Meteor track}

	\cite{davies1994thermomechanical} described a process of thermo-mechanical erosion which involves heating-softening of the lithospheric base by a plume tail, followed by mechanical removal of the material due to convective transfer. \citep{rondenay2000lithospheric}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SECTION FOR FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Figure}

	% Geological Map
	\begin{figure}

		\centering
		\centerline{\includegraphics[viewport=180 340 480 570,clip=true,width=\linewidth]{figures/Geologicalmap_Clouzet.pdf}}

		% bb=llx lly urx ury :
		\caption{\baselineskip 18pt
		Large scale Precambrian architecture of North America (modified from \cite{whitmeyer2007tectonic}. Colours indicate ages of different regions, as shown in the legend. The stable cratonic core is defined by the Rocky Mountain Front to the west (dashed dark grey line), defined by the surface trace of deformation), and the appalachian fron to the east (solid light red line). The solid blue line demarcates the westward extent of the Grenville/Llano Front. The solid red line along the Cordillera province demarcates the breakup of Rodinia. Solid green lines indicate tectonic plate boundaries. Abreviations are as follows: RW, re-worked; GBA, Great Bear Arc; BHT, Buffalo Head Terrane; Taltson, Talston Arc; Rimbey, Rimbey Arc; Tornagat, Torngat Arc; L.B.A, Little Belt Arc; LRA; THO, Trans-Hudson Orogen; RGR, Rio Grande Rift; Reelfoot, Reelfoor Rift; Kwn.R, Kewanowan Rift; Sask, Sask Craton; WY, Wyoming Province; Med. Hat., Medicine Hat Block; Grt. Rhy, Granite–Rhyolite Province; Grenville, Grenville Province.
		}

	% Map of events and stations
	\begin{figure}
		\centering
		\begin{tabular}{ccc}
			\includegraphics[width=1\textwidth]{figures/map_events_stn_global.png}
		\end{tabular}

	 % Density coverage
	\begin{figure}
		\begin{minipage}{0.47\linewidth}
			\centerline{\includegraphics[viewport=120 10 470 420,clip=,width=\linewidth]{figures/Coverage_L_iter3.png}}
		\end{minipage}
		\hfill
		\begin{minipage}{0.47\linewidth}
			\centerline{\includegraphics[viewport=120 10 470 420,clip=,width=\linewidth]{figures/Coverage_T_iter3.png}}
		\end{minipage}

	% Box Tomo
	\begin{figure}
		\begin{tabular}{ccc}
			(a)&&(b)\\
			\includegraphics[width=.4\textwidth]{figures/snap_glob.pdf} && \includegraphics[width=.4\textwidth]{figures/snap_reg.pdf} \\ 
			\includegraphics[width=.4\textwidth]{figures/seismo.pdf}    && \includegraphics[width=.4\textwidth]{figures/seismo.pdf}
		\end{tabular}

	 % 3d map of Vs
	\begin{figure}
		\centering
		\includegraphics[width=1\textwidth]{figures/Vs-60-300-for-paper.png}

		\caption{\baselineskip 18pt
		3D isotropic shear wave velocity structure of the continent. Map views are shown from 60 km down to 300 km, as variations with respect to the regional mean (thick red line in Figure ~\ref{1daverage}) as $\frac{dV_S}{V_{S_{O}}}$ . 
		Below each map, depth and its regional shear velocity mean is indicated. Minimum and maximum perturbations are also indicated.
		}

	% 3d map of Xi
	\begin{figure}
		\centering
		\includegraphics[width=1\textwidth]{figures/Xi-60-300-for-paper.png}

		\caption{\baselineskip 18pt
		3D radial anisotropic structure of the continent. Map views are shown from 60 km down to 300 km, as variations with respect to the regional mean (thick red line in Figure ~\ref{1daverage}) as $\frac{d\xi}{\xi_{O}}$ . 
		Below each map, depth and its regional shear velocity mean is indicated. Minimum and maximum perturbations are also indicated.
		}

	% 1D profiles
	\begin{figure}
		\centering
		\includegraphics[width=1\textwidth]{figures/1D_profile_with_regions.png}

	% Xsections of the craton
	\begin{figure}
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_A.pdf}}
		\end{minipage}
		\hfill
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_B.pdf}}
		\end{minipage}

@@

@@

	% Xsection of the GMT track
	\begin{figure}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_GMTrack.pdf}}

@@

	% dIso for Xi
	\begin{figure}
		\centerline{\includegraphics[width=\linewidth]{figures/Xi_NASEM-iter3-Xi-iso_100km.png}}

		\caption{3D radial anisotropic structure of the continent at 100km compared to the Isotroic case. 
		Map view shows variations with respect to the Isotropic case as $\frac{\xi - 1}{1}$ in \%. 
		Map view is saturated to better show where $V_{SV}$ is stronger than $V_{SH}$.
		Below each map, depth and its regional shear velocity mean is indicated. Minimum and maximum perturbations are also indicated.}
		\label{3d-xi-iso-100km}

	\end{figure}
\bibliographystyle{apalike}
\bibliography{/Users/Pierre/Documents/PHD/Thesis/biblio.bib}
%
\end{document}
